---
title: '"W3-Day3-Loan Study Writeup"'
author: "Thoa & Ro"
date: "June 28, 2017"
output: html_document
---
Contact info: MSR-DS3 2017

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
load("hw3-outputs.RData")
```

## Introduction
This is a template for a write-up. You can see more advanced ones [here](http://rmarkdown.rstudio.com/developer_document_templates.html) and [here](http://rmarkdown.rstudio.com/gallery.html).

## Data
We used data from Kaggle: https://www.kaggle.com/zhijinzhai/loandata

## Hypotheses
These are our scientific hypotheses and why they are interesting or important.

## Analyses
We analyzed the data and made these figures.


```{r plot, echo=FALSE}
plot(cnt_loanstatus_by_edu)
plot(pct_loanstatus_by_edu)
plot(cnt_loanstatus_by_age)
plot(loanstatus_at_age_and_edu)
plot(pct_term_used_and_principal)
plot(pct_term_used_dist_by_principal)
plot(pct_term_used_and_id)
```

We don't have any variables to include in text, but if yes, we can output it by typing r variable_name.

## Discussion
We think we did a great job. We think this means that.

## Appendix
More details about the data: this data set is small, just around 500 observations. It is about people borrowing bullet loans. A bullet loan is a financial product that requires one-time pay-off, instead of an installment schedule. Loan status can be (1) paid off, (2) paid off after being put in collection, and (3) never paid off even after being in collection.

We (hypothetically) registered the study at AsPredicted.